Bird beak's elaboration and innovation

### 2022-05-25 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

>>>>

```{r, eval = TRUE, echo = FALSE}
## Load the data
load(file = "../Data/Processed/shapsepace_passeriformes_suborder_family.rda")
## Select the data
shapespace <- shapsepace_passeriformes_suborder_family[[1]]$space
tree <- shapsepace_passeriformes_suborder_family[[1]]$consensus_tree
## Clean garbage
rm(shapsepace_passeriformes_suborder_family)

## Load the covar
load(file = "../Data/Processed/shapespace_passeriformes.MCMCglmm")
shapespace_passeriformes <- shapespace_passeriformes[[1]]

## Get the levels
phylo_lvl <- which(MCMCglmm.levels(shapespace_passeriformes) == "animal")
suborder_lvl <- grep("level1_", MCMCglmm.levels(shapespace_passeriformes))
family_lvl <- grep("level2_", MCMCglmm.levels(shapespace_passeriformes))

## Creating the subsets
suborder_shapespace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
      data          = shapespace,
      posteriors    = shapespace_passeriformes,
      group         = MCMCglmm.levels(shapespace_passeriformes)[c(suborder_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level1)[-1], "phylogeny")) #[-1] is because the first level is ""

family_shapespace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
      data          = shapespace,
      posteriors    = shapespace_passeriformes,
      group         = MCMCglmm.levels(shapespace_passeriformes)[c(family_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_passeriformes)
```

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE, results = 'hide', message = FALSE, warning = FALSE}
## Run the analyses between groups
suborder_results_between <- dispRity.covar.projections(suborder_shapespace,
                                             type = "groups",
                                             base = "phylogeny",
                                             verbose = TRUE,
                                             output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses between groups
family_results_between <- dispRity.covar.projections(family_shapespace,
                                             type = "groups",
                                             base = "phylogeny",
                                             verbose = TRUE,
                                             output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses of groups on the phylogeny
suborder_results_phylo <- dispRity.covar.projections(suborder_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)

## Run the analyses of groups on the phylogeny
family_results_phylo <- dispRity.covar.projections(family_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses groups on themselves
suborder_results_within <- dispRity.covar.projections(suborder_shapespace,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses groups on themselves
family_results_within <- dispRity.covar.projections(family_shapespace,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
shapespace_passeriformes_suborder_family_results_list <- list(
        "suborder_results_between" = suborder_results_between,
        "family_results_between"   = family_results_between,
        "suborder_results_phylo"   = suborder_results_phylo,
        "family_results_phylo"     = family_results_phylo,
        "suborder_results_within"  = suborder_results_within,
        "family_results_within"    = family_results_within)
save(shapespace_passeriformes_suborder_family_results_list, file = "../Data/Processed/shapespace_passeriformes_suborder_family_results_list.rda")
```
